CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-10-01 codecheck-paper.tex
extend text in limitations, add notes for future work

\textbf{Handling failure}: we have no established process for this, as
so far all our codechecks succeeded. Open question remains as what to do
in this case -- should we publicly report that the code would not run.

\textbf{Compute time}: for those papers that take significant compute
time (think days, not minutes), who will pay for the compute time?

@@

\textbf{Can't someone cheat?} yes. we don't check it is correct code,
just simply that it runs. Very low bar. But by having the code open,
interested parties can then examine the code, and knowing that the code
will be open we hope will be an incentive for authors to share.

@@

\begin{itemize}
\item
  possibility to allow CI for open papers such that for ``nearly free''
  we can find out when softwave breaks, and if provenance tools are
  used, when.
\item
  How to embed this in journals.
\item
  When is CODECHECK redundant? will it become part of regular peer
  review? or, if ayuthors become more skillful, then everything becomes
  automated, and no need for codecheck. CODECHECK disappearing is then a
  measure of success.
\end{itemize}

>>>>

\textbf{Just peer review}: Wait, isn't that what peer review should be 
doing already? That is correct.
The general observation is that the increasing
number of researchers, submissions, and reviews to conduct under the
pressure to publish, puts the scholarly publication system under a lot
of strain [REF].  We also see parallels to the terms 
`reproducible research' and `open science'. Establishing a CODECHECK 
process is largely an acknowledgement that peer reviewing practices 
have faltered to adopt to the challenges of digitisation and computer-based
research or data science. The concept of a CODECHECK, just as the 
reproducibility of research and the openness of science, may be of 
transitional nature. If the activites described here as being part of a 
CODECHECK become the norm for scientific reviews and publications, then
the initiative will have succeeded.
However, the rapidly changing technology used in  research leads us to 
believe that a seperate role of codechecker is benefitial in general.

\textbf{Handling failure}: we have no established process for this, as
so far all our codechecks succeeded. Open question remains as what to do
in this case -- should we publicly report that the code would not run.
Be careful as to the impact of acceptance or volunteers this decision
has.

\textbf{Compute time}: for those papers that take significant compute
time (think days, not minutes), who will pay for the compute time?
The openness of CODECHECK certificates could help to establish community
peer pressure, as submitting authors can be evaluated on their engagement
as codecheckers.

@@

\textbf{Can't someone cheat?} Yes. we don't check it is correct code,
just simply that it runs. This `mechanical' test is indeed a very low bar.
Yet, by having the code and data openly deposited, interested parties can
then examine the code, and knowing that the code will be open we hope will
be an incentive for authors to share. It will also give the opportunity 
to future researchers, potentially with new methods, to look for errors.
This is a much more effective means to avoid cheating than an arms race
trying to catch the cheater with closed datasets and code.
% give credit to Everything Hertz podcast for the idea? they compared it
% to the blood samples of drug tests in sports (stored for n years)

@@

\begin{itemize}
\item
  CODECHECK works! we have created 23 certificates to demonstrate it.
\item 
  CODECHECK and can increase trust in results, underlies the same
  limitations as peer review (needs people with time), but also the same
  power (community, reasoning of human)
\item
  possibility to allow CI for open papers such that for ``nearly free''
  we can find out when softwave breaks, and if provenance tools are
  used, when.
\item
  How to embed this in journals.
\item
  When some journals have it - what are crucial decisions/pain points?
  How open do they make the check itself and its outputs, and how does it
  relate/influence the openness of regular peer review
\item
  When is CODECHECK redundant? will it become part of regular peer
  review? or, if ayuthors become more skillful, then everything becomes
  automated, and no need for codecheck. CODECHECK disappearing is then a
  measure of success.
\end{itemize}
